Urban and socio-economic correlates of property price evolution\:\ Application to Dublin's costal area

### 2020-08-14 manuscript/manuscript.Rmd
reviewer answer startup

bibliography: [references.bib, r-references.bib]
output:
  bookdown::pdf_book:
    base_format: rticles::ieee_article

@@

# functions --------------------------------------------------------------------
source(here::here("script/functions_project.R"))
source(here::here("script/osm_dublin_features.R"))
# data path --------------------------------------------------------------------
data_path <- here::here() %>% 
  dirname() %>% 
  dirname() %>% 
  paste0("/data/property_price_ireland_data")

>>>>

bibliography: ["bib/references.bib", "bib/r-references.bib"]
output:
  bookdown::pdf_book:
    base_format: rticles::ieee_article

@@

# functions --------------------------------------------------------------------
source(here::here("script/functions_project.R"))
source(here::here("script/osm_dublin_features.R"))

# data path --------------------------------------------------------------------
data_path <- here::here() %>% 
  dirname() %>% 
  dirname() %>% 
  paste0("/data/property_price_ireland_data")
